Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-03-26 parts/def-ph.tex
minor updates

\pref{def:substate} defines the notion of sub-state on a set of sorts,
that is used to consider the interesting part of a complete state.
\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
\label{def:substate}
  If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
  $\PHsubl[\PHl]_S \DEF \{ \mysigma \in \bigtimes{a \in S} \PHl_a \}$.
  The set of all sub-sets is:
  $\PHsubl[\PHl] \DEF \bigcup_{S \subset \PHs} \PHsubl[\PHl]_S$.

@@

In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
\begin{definition}[Well-formed component ($\components$)]
\label{def:component}
  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
  \begin{align*}
    \forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2 \enspace.
  \end{align*}
  We call $\components$ the set of well-formed components.
\end{definition}

>>>>

\pref{def:substate} defines the notion of sub-state on a set of sorts,
that is used to consider the interesting part of a complete state.
\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
\label{def:substate}
  If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
  $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
  The set of all sub-sets is:
  $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.

@@

In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
\begin{definition}[Well-formed component]
\label{def:component}
  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
  We denote $\components\subset\Sigma$ the set of well-formed components.
\end{definition}
